\Title

### 2023-02-09 Grimaldi-etal-BiolCybernetics.tex
methods : caption

    {\bf - Motion detection task.} {\bf (left)}~We use large natural images ($512\times512$) in which an aperture ($128\times128$) extracts a cropped  image around the axis of view. To mimic the effect of a saccadic eye movement, the view axis moves according to a stepwise random walk, and we show an example path of the trajectory as a green line ($200$ time steps). {\bf (right)}~Snapshot of the synthetic event stream at different time steps. The dynamics of the sub-image as a function of time generates a naturalistic film. This can be transformed into an event-based representation. Mimicking the retina, this representation encodes proportional and pixel-wise increases or decreases in luminance in the image, respectively ON (red) and OFF (blue) events. In the lower left corner of the images, the translation vector is shown in red. It is one of the possible classes of motion. Note the change in the direction of motion between the second and the third image.}

>>>>

        {\bf - Motion Detection Task.} {\bf (left)}~We use large natural images ($512\times512$) in which an aperture ($128\times128$) extracts a cropped image around the view axis. To mimic the effect of a saccadic eye movement, the view axis moves according to a stepwise random walk. We show an example path of the trajectory for $200$ time steps (green line). {\bf (right)}~Snapshot of the synthetic event stream at different time steps. The dynamics of the sub-image as a function of time produces a naturalistic movie. This can be transformed into an event-based representation. Mimicking the retina, this representation encodes proportional and pixel-wise increases or decreases in luminance in the image, i.e. ON (red) and OFF (blue) events. In the lower left corner of the images, the translation vector is shown in red. It is one of the possible classes of motion. Note the change in the direction of motion between the second and third image.}
